The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-09-06 analysis/paper/paper.qmd
Update code chunk options
Some code chunks do not run and prevent rendering. I temporarily made them inactive with eval: false.

```{r fig-process-diagram}
#| fig-cap: Text mining process

@@

```{r topics-per-corpus}

@@

```{r lda-vis}

@@

# Extract topics as mixtures of terms from LDA model
emu_topics <- tidy(emu_lda, matrix = "beta")

@@

```{r topic-model-gamma}

# Extract documents as mixtures of topics from LDA model
emu_documents <- tidy(emu_lda, matrix = "gamma")

@@

emu_documents |> 
  inner_join(emu |> 
               select(title, graduation_year), 
             by = c("document" = "title")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)

@@

```{r top-words-document}

# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, top_n = 10)
```

@@

## Calculate tf-idf statistic
emu_tf_idf <- emu_words |> 
  get_tf_idf(title_col = "title", word_col = "word")

## Get top n words most specific to each thesis 
emu_tf_idf |> 
  group_by(title) |> 
  top_n(5, tf_idf) |> 
  arrange(desc(tf_idf), .by_group = TRUE)

@@

## Visualise the top n words with the highest tf-idf values for each of a subset of theses
emu_words_count |> 
  get_tf_idf(title_col = "title", word_col = "word") |> 
  filter(title == unique(title)[1:2]) |>  # Keep only the first 6 theses
  arrange(desc(tf_idf)) |> 
  mutate(word = factor(word, levels = rev(unique(word)))) |> 
  group_by(title) |> 
  top_n(15) |> 
  ungroup() |> 
  ggplot(aes(word, tf_idf, fill = title)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~ title,  ncol = 3, scales = "free") +
  coord_flip()
```

@@

\[Describe word embeddings ...\]

@@

# To what extent do words co-occur with other words?
tidy_pmi <- get_pmi(emu, title_col = "title", text_col = "text_clean")
```

@@

\[What terms should be checked with the function below?\]

@@

The first \[?\] components... \[what do they show?\]

@@

-   Although the focus of this study is on describing a fixed corpus though unsupervised machine learning, it can provide input into supervised predictive models.

>>>>

```{r fig-process-diagram}
#| fig-cap: Text mining process
#| eval: false

@@

```{r topics-per-corpus}
#| eval: false

@@

```{r lda-vis}
#| eval: false

@@

# Extract topics as mixtures of terms from LDA model
emu_topics <- tidy(emu_lda_5, matrix = "beta")

@@

```{r topic-model-gamma}
#| eval: false

# Extract documents as mixtures of topics from LDA model
emu_documents <- tidy(emu_lda_5, matrix = "gamma")

@@

emu_documents |>
  mutate(document = as.numeric(document)) |> 
  inner_join(emu |> 
               select(ID, graduation_year), 
             by = c("document" = "ID")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)

@@

```{r top-words-document}
#| eval: false

# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, title_col = "ID", top_n = 10)
```

@@

## Calculate tf-idf statistic
emu_tf_idf <- emu_words |> 
  get_tf_idf(title_col = "ID", word_col = "word")

## Get top n words most specific to each thesis 
emu_tf_idf |> 
  group_by(ID) |> 
  top_n(5, tf_idf) |> 
  arrange(desc(tf_idf), .by_group = TRUE)

@@

## Visualise the top n words with the highest tf-idf values for each of a subset of theses
emu_words_count |> 
  get_tf_idf(title_col = "ID", word_col = "word") |> 
  filter(ID == unique(ID)[1:2]) |>  # Keep only the first 6 theses
  arrange(desc(tf_idf)) |> 
  mutate(word = factor(word, levels = rev(unique(word)))) |> 
  group_by(ID) |> 
  top_n(15) |> 
  ungroup() |> 
  ggplot(aes(word, tf_idf, fill = ID)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~ ID,  ncol = 3, scales = "free") +
  coord_flip()
```

@@

Describe word embeddings ...

@@

# To what extent do words co-occur with other words?
tidy_pmi <- get_pmi(emu, title_col = "ID", text_col = "text_clean")
```

@@

What terms should be checked with the function below?

@@

The first # components... what do they show?

@@

Although the focus of this study is on describing a fixed corpus though unsupervised machine learning, it can provide input into supervised predictive models.
